Simulating the Linux page cache in distributed applications with WRENCH

### 2020-12-10 paper_io_sim.tex
Typo

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
\usepackage{graphicx}
\usepackage{algorithm}
\usepackage{algorithmicx}
\usepackage{algpseudocode}
\usepackage[dvipsnames]{xcolor}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{ulem}
\usepackage{tabularx}

@@

\author{\IEEEauthorblockN{Hoang-Dung Do$^1$, Val\'erie Hayot-Sasson$^1$, Rafael Ferreira da Silva$^3$, Henri Casanova$^2$, Tristan Glatard$^1$
  }\\
  \IEEEauthorblockA{
    $^1$Department of Computer Science and Software Engineering, Concordia University, Montreal, Canada\\
     $^2$Department of Information and Computer Sciences, University of Hawai`i at M\=anoa, USA\\
     $^3$Department of Computer Science, University of Southern California, Los Angeles, USA
  }
}

@@

	In this work, we present WRENCH-cache, a simulation model of I/O
	with page cache incorporated into the WRENCH simulation framework~\cite{casanova2018wrench},
	which is  based on the popular SimGrid distributed simulation framework~\cite{XXX}.
	WRENCH-cache is to make it possible to simulate 
        application execution accurately in the presence of page caching. Our specific 
        contributions are as follows:
    \begin{compactitem}
        \item A page cache simulation model that supports 
	both single-threaded and multithreaded applications, and of both
	writeback and writethrough caches for local or network-based
	filesystems;
        \item An implementation of this model as part of the WRENCH framework; 
        \item An evaluation and validation of the accuracy of our model, and of its implementation,
              for a range of applications, platforms, and page cache configurations. 
    \end{compactitem}

>>>>

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
\usepackage{graphicx}
\usepackage{paralist}
\usepackage{algorithm}
\usepackage{algorithmicx}
\usepackage{algpseudocode}
\usepackage[dvipsnames]{xcolor}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{ulem}
\usepackage{tabularx}

@@

\author{
  \IEEEauthorblockN{
    Hoang-Dung Do\IEEEauthorrefmark{1},
    Val\'erie Hayot-Sasson\IEEEauthorrefmark{1},
    Rafael Ferreira da Silva\IEEEauthorrefmark{3},
    Henri Casanova\IEEEauthorrefmark{2},
    Tristan Glatard\IEEEauthorrefmark{1}
  }\\
  \IEEEauthorblockA{
    \IEEEauthorrefmark{1}Department of Computer Science and Software Engineering, Concordia University, Montreal, Canada\\
    \IEEEauthorrefmark{2}Department of Information and Computer Sciences, University of Hawai`i at M\=anoa, USA\\
    \IEEEauthorrefmark{3}Information Sciences Institute, University of Southern California, Marina Del Rey, CA, USA
  }
}

@@

	In this work, we present WRENCH-cache, a simulation model of I/O
	with page cache incorporated into the WRENCH simulation framework~\cite{casanova2018wrench},
	which is  based on the popular SimGrid distributed simulation framework~\cite{XXX}.
	The added value of WRENCH-cache is to make it possible to simulate 
        application execution accurately in the presence of page caching. Our specific 
        contributions are as follows:
    \begin{compactitem}
        \item A page cache simulation model that supports 
	both single-threaded and multithreaded applications, and of both
	writeback and writethrough caches for local or network-based
	filesystems;
        \item An implementation of this model as part of the WRENCH framework; 
        \item An evaluation and validation of the accuracy of our model, and of its implementation,
              for a range of applications, platforms, and page cache configurations. 
    \end{compactitem}
